Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-07-21 paper/paper.tex
Working on generating manipulations figures

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_wt.png}
\caption{Gradient following model with axon-axon interactions.}
\label{f:wt}
\end{figure}

@@

To determine if the model can explain the many surgical and genetic
manipulations described in the literature
\citep*[for a review, see][]{goodhill_retinotectal_1999} we performed
simulations matching those in \citet{simpson_simple_2011} where we either
rotated or translocated grafts of the tectum, ablated portions of the retina
and/or the tectum or manipulated the receptor or ligand expressions in the
model...

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_wt_fig.png}
\caption{Gradient following model with axon-axon interactions.}
\label{f:wt}
\end{figure}

\subsection*{Normal development}

@@

To determine if the model can explain the many surgical and genetic
manipulations described in the literature
\citep*[for a review, see][]{goodhill_retinotectal_1999} we performed
simulations matching those in \citet{simpson_simple_2011} in which we either
rotated or translocated grafts of the tectum; ablated portions of the retina
and/or the tectum; or manipulated the receptor or ligand expressions in the
model.

\begin{figure}
\includegraphics[width=\linewidth]{./images/fig_manipulations.png}
\caption{Surgical manipulations}
\label{f:manip}
\end{figure}
